---
title: "Analysis Report"
author: "Fatima Zulfiqar"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: cerulean
---

## Introduction
This document performs basic analysis of the World Happiness Report 2024 dataset in R, including data loading, summary statistics, missing value identification, and saving the cleaned dataset.

## Load Required Libraries

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Install and load necessary packages
if(!require(readr)) install.packages("readr", dependencies=TRUE)
library(readr)
```

## Load Dataset

```{r load_data, echo=TRUE}
# Load dataset
data <- read_csv("C:/Users/Dell/Downloads/World happiness report/WHR2024.csv")

# Show first 5 rows
head(data, 5)
```

## Summary Statistics

```{r summary_stats, echo=TRUE}
# Display summary statistics
summary(data)
```

## Identify Missing Values

```{r missing_values, echo=TRUE}
# Count missing values in each column
colSums(is.na(data))
```

## Save Cleaned Data

```{r save_data, echo=TRUE}
# Save cleaned dataset
write.csv(data, "cleaned_happiness.csv", row.names = FALSE)
```

## Conclusion

This analysis includes data loading, summary statistics, missing value detection, and saving the cleaned dataset for further analysis.
